Mallows, Black-box combinatorial optimization, limited budget, ???

### 2020-09-07 paper/main.tex
update cpu info.

\manuel{Computing system details: MANUEL}{%
  All experiments were run on Intel Xeon E5-2640 CPUs at 2.50\,GHz, 64\,GB RAM
  running CentOS Linux release 7.4.1708 (Core).  }

>>>>

\manuel{Computing system details: MANUEL}{%
  All experiments were run on Intel Xeon ``Ivybridge'' E5-2650v2 CPUs at 2.60\,GHz, 64\,GB RAM
  running CentOS Linux release 7.4.1708 (Core).  }
